Notes on \\ Projected Knowledge Compilation \\ \today

### 2023-08-08 doc/pkc-notes.tex
Minor tweaks

\item[$\ureduce{\phi}{x}$:] Express the universal quantification of $\phi$ with respect to variable $x$ in clausal form, by removing all occurrences of $x$ and $\obar{x}$:
$\ureduce{\phi}{x} = \lfilter(\phi, \{x, \obar{x}\})$.

>>>>

\item[$\ureduce{\phi}{x}$:] Express the universal quantification of $\phi$ with respect to variable $x$ in clausal form.  This involves removing all occurrences of $x$ and $\obar{x}$:
$\ureduce{\phi}{x} = \lfilter(\phi, \{x, \obar{x}\})$.
